\begin{thebibliography}{}

\bibitem[Chavula et~al., 2012]{chavula_stopping_2012}
Chavula, C., \textbf{Long, D.M.}, Mzembe, E., Kayira, D., Chasela, C., Hudgens, M.~G.,
  Hosseinipour, M., King, C.~C., Ellington, S., Chigwenembe, M., Jamieson,
  D.~J., and van~der Horst, C. (2012).
\newblock Stopping the control arm in response to the {DSMB}: mother's choice
  of {HIV} prophylaxis during breastfeeding in the {BAN} {Study}.
\newblock {\em Contemporary clinical trials}, 33(1):55--59.
\newblock Place: United States.

\bibitem[Heil et~al., 2012]{heil_impact_2012}
Heil, E.~L., Daniels, L.~M., \textbf{Long, D.M.}, Rodino, K.~G., Weber, D.~J., and
  Miller, M.~B. (2012).
\newblock Impact of a rapid peptide nucleic acid fluorescence in situ
  hybridization assay on treatment of {Candida} infections.
\newblock {\em American journal of health-system pharmacy : AJHP : official
  journal of the American Society of Health-System Pharmacists},
  69(21):1910--1914.
\newblock Place: England.

\bibitem[Long and Hudgens, 2012]{long_comparing_2012}
\textbf{Long, D.M.} and Hudgens, M.~G. (2012).
\newblock Comparing competing risk outcomes within principal strata, with
  application to studies of mother-to-child transmission of {HIV}.
\newblock {\em Statistics in medicine}, 31(27):3406--3418.
\newblock Place: England.

\bibitem[Long and Hudgens, 2013]{long_sharpening_2013}
\textbf{Long, D.M.} and Hudgens, M.~G. (2013).
\newblock Sharpening bounds on principal effects with covariates.
\newblock {\em Biometrics}, 69(4):812--819.
\newblock Place: United States.

\bibitem[Misra et~al., 2013]{misra_relationship_2013}
Misra, R., Chandra, P., Riechman, S.~E., \textbf{Long, D.M.}, Shinde, S., Pownall,
  H.~J., Coraza, I., Lewis, D.~E., Sekhar, R.~V., and Balasubramanyam, A.
  (2013).
\newblock Relationship of ethnicity and {CD4} {Count} with glucose metabolism
  among {HIV} patients on {Highly}-{Active} {Antiretroviral} {Therapy}
  ({HAART}).
\newblock {\em BMC endocrine disorders}, 13:13.
\newblock Place: England.

\bibitem[Con et~al., 2014]{con_falls_2014}
Con, J., Friese, R.~S., \textbf{Long, D.M.}, Zangbar, B., O'Keeffe, T., Joseph, B.,
  Rhee, P., and Tang, A.~L. (2014).
\newblock Falls from ladders: age matters more than height.
\newblock {\em The Journal of surgical research}, 191(2):262--267.
\newblock Place: United States.

\bibitem[Croston et~al., 2014]{croston_functional_2014}
Croston, T.~L., Thapa, D., Holden, A.~A., Tveter, K.~J., Lewis, S.~E.,
  Shepherd, D.~L., Nichols, C.~E., \textbf{Long, D.M.}, Olfert, I.~M., Jagannathan, R.,
  and Hollander, J.~M. (2014).
\newblock Functional deficiencies of subsarcolemmal mitochondria in the type 2
  diabetic human heart.
\newblock {\em American journal of physiology. Heart and circulatory
  physiology}, 307(1):H54--65.
\newblock Place: United States.

\bibitem[Fink-Miller et~al., 2014]{fink-miller_comparing_2014}
Fink-Miller, E.~L., \textbf{Long, D.M.}, and Gross, R.~T. (2014).
\newblock Comparing chronic pain treatment seekers in primary care versus
  tertiary care settings.
\newblock {\em Journal of the American Board of Family Medicine : JABFM},
  27(5):594--601.
\newblock Place: United States.

\bibitem[Akbar et~al., 2015]{akbar_hyperuricemia_2015}
Akbar, S.~R., \textbf{Long, D.M.}, Hussain, K., Alhajhusain, A., Ahmed, U.~S., Iqbal,
  H.~I., Ali, A.~W., Leonard, R., and Dalton, C. (2015).
\newblock Hyperuricemia: {An} {Early} {Marker} for {Severity} of {Illness} in
  {Sepsis}.
\newblock {\em International journal of nephrology}, 2015:301021.
\newblock Place: United States.

\bibitem[Con et~al., 2015]{con_secondary_2015}
Con, J., \textbf{Long, D.M.}, Sasala, E., Khan, U., Knight, J., Schaefer, G., and Wilson,
  A. (2015).
\newblock Secondary overtriage in a statewide rural trauma system.
\newblock {\em The Journal of surgical research}, 198(2):462--467.
\newblock Place: United States.

\bibitem[Long et~al., 2015]{long_surrogates_2015}
\textbf{Long, D.M.}, Hudgens, M.~G., and Wu, C.-D. (2015).
\newblock Surrogates of protection in repeated low-dose challenge experiments.
\newblock {\em Statistics in medicine}, 34(10):1747--1760.
\newblock Place: England.

\bibitem[Mallow et~al., 2015]{mallow_study_2015}
Mallow, J.~A., Theeke, L.~A., \textbf{Long, D.M.}, Whetsel, T., Theeke, E., and Mallow,
  B.~K. (2015).
\newblock Study protocol: mobile improvement of self-management ability through
  rural technology ({mI} {SMART}).
\newblock {\em SpringerPlus}, 4:423.
\newblock Place: Switzerland.

\bibitem[Schmidt et~al., 2015]{schmidt_power_2015}
Schmidt, R.~J., Weaner, B.~B., and \textbf{Long, D.M.} (2015).
\newblock The power of advance care planning in promoting hospice and out-of-
  hospital death in a dialysis unit.
\newblock {\em Journal of palliative medicine}, 18(1):62--66.
\newblock Place: United States.

\bibitem[Baus et~al., 2016]{baus_developing_2016}
Baus, A., Zullig, K., \textbf{Long, D.M.}, Mullett, C., Pollard, C., Taylor, H., and
  Coben, J. (2016).
\newblock Developing {Methods} of {Repurposing} {Electronic} {Health} {Record}
  {Data} for {Identification} of {Older} {Adults} at {Risk} of {Unintentional}
  {Falls}.
\newblock {\em Perspectives in health information management}, 13:1b.
\newblock Place: United States.

\bibitem[Conway et~al., 2016a]{conway_perfluoroalkyl_2016}
Conway, B., Innes, K.~E., and \textbf{Long, D.M.} (2016a).
\newblock Perfluoroalkyl substances and beta cell deficient diabetes.
\newblock {\em Journal of diabetes and its complications}, 30(6):993--998.
\newblock Place: United States.

\bibitem[Conway et~al., 2016b]{conway_glycemic_2016}
Conway, B.~N., \textbf{Long, D.M.}, Figaro, M.~K., and May, M.~E. (2016b).
\newblock Glycemic control and fracture risk in elderly patients with diabetes.
\newblock {\em Diabetes research and clinical practice}, 115:47--53.
\newblock Place: Ireland.

\bibitem[Denney et~al., 2016]{denney_validating_2016}
Denney, M.~J., \textbf{Long, D.M.}, Armistead, M.~G., Anderson, J.~L., and Conway,
  B.~N. (2016).
\newblock Validating the extract, transform, load process used to populate a
  large clinical research database.
\newblock {\em International journal of medical informatics}, 94:271--274.
\newblock Place: Ireland.


\bibitem[Kudo et~al., 2016]{kudo_surgical_2016}
Kudo, Y.~K., Davis, L.~V., \textbf{Long, D.M.}, Honaker, J.~C., and Nakayama, D.~K.
  (2016).
\newblock Surgical {Care} {Improvement} {Project} {Measures} among {Rural} and
  {Urban} {Hospitals} in {West} {Virginia}.
\newblock {\em The American surgeon}, 82(1):E20--22.
\newblock Place: United States.

\bibitem[Leung et~al., 2016]{leung_pediatric_2016}
Leung, A., Bonasso, P., Lynch, K., \textbf{Long, D.M.}, Vaughan, R., Wilson, A., and Con,
  J. (2016).
\newblock Pediatric {Secondary} {Overtriage} in a {Statewide} {Trauma}
  {System}.
\newblock {\em The American surgeon}, 82(9):763--767.
\newblock Place: United States.

\bibitem[Lynch et~al., 2016]{lynch_nationwide_2016}
Lynch, K.~T., Essig, R.~M., \textbf{Long, D.M.}, Wilson, A., and Con, J. (2016).
\newblock Nationwide secondary overtriage in level 3 and level 4 trauma
  centers: are these transfers necessary?
\newblock {\em The Journal of surgical research}, 204(2):460--466.
\newblock Place: United States.

\bibitem[Shepherd et~al., 2016]{shepherd_early_2016}
Shepherd, D.~L., Nichols, C.~E., Croston, T.~L., McLaughlin, S.~L., Petrone,
  A.~B., Lewis, S.~E., Thapa, D., \textbf{Long, D.M.}, Dick, G.~M., and Hollander,
  J.~M. (2016).
\newblock Early detection of cardiac dysfunction in the type 1 diabetic heart
  using speckle-tracking based strain imaging.
\newblock {\em Journal of molecular and cellular cardiology}, 90:74--83.
\newblock Place: England.

\bibitem[Baus et~al., 2017]{baus_electronic_2017}
Baus, A., Coben, J., Zullig, K., Pollard, C., Mullett, C., Taylor, H., Cochran,
  J., Jarrett, T., and \textbf{Long, D.M.} (2017).
\newblock An {Electronic} {Health} {Record} {Data}-driven {Model} for
  {Identifying} {Older} {Adults} at {Risk} of {Unintentional} {Falls}.
\newblock {\em Perspectives in health information management}, 14(Fall):1b.
\newblock Place: United States.

\bibitem[Bonasso et~al., 2017]{bonasso_effect_2017}
Bonasso, P., Lucke-Wold, B.~P., Riffon, M., \textbf{Long, D.M.}, Wilson, A., and Knight,
  J. (2017).
\newblock The {Effect} of {Sporting} {Events} on {Medical} {Transport} {Time}
  at a {Level} 1 {Trauma} {Center}: a {Retrospective} {Cohort} {Study}.
\newblock {\em The West Virginia medical journal}, 113(3):44--51.
\newblock Place: United States.

\bibitem[Ducatman et~al., 2017]{ducatman_quality_2017}
Ducatman, A.~M., Tacker, D.~H., Ducatman, B.~S., \textbf{Long, D.M.}, Perrotta, P.~L.,
  Lawther, H., Pennington, K., Lander, O., Warden, M., Failinger, C.,
  Halbritter, K., Pellegrino, R., Treese, M., Stead, J.~A., Glass, E.,
  Cianciaruso, L., and Nau, K.~C. (2017).
\newblock Quality {Improvement} {Intervention} for {Reduction} of {Redundant}
  {Testing}.
\newblock {\em Academic pathology}, 4:2374289517707506.
\newblock Place: United States.

\bibitem[Graf et~al., 2017]{graf_successful_2017}
Graf, A.~S., \textbf{Long, D.M.}, and Patrick, J.~H. (2017).
\newblock Successful aging across adulthood: {Hassles}, uplifts, and
  self-assessed health in daily context.
\newblock {\em Journal of Adult Development}, 24:216--225.
\newblock Publisher: Springer US.

\bibitem[Lutz et~al., 2017]{lutz_predicting_2017}
Lutz, J., Gross, R., \textbf{Long, D.M.}, and Cox, S. (2017).
\newblock Predicting {Risk} for {Opioid} {Misuse} in {Chronic} {Pain} with a
  {Single}-{Item} {Measure} of {Catastrophic} {Thinking}.
\newblock {\em Journal of the American Board of Family Medicine : JABFM},
  30(6):828--831.
\newblock Place: United States.

\bibitem[Wietholter et~al., 2017]{wietholter_perceived_2017}
Wietholter, J.~P., Ponte, C.~D., and \textbf{Long, D.M.} (2017).
\newblock The perceived value of clinical pharmacy service provision by
  pharmacists and physicians: an initial assessment of family medicine and
  internal medicine providers.
\newblock {\em The International journal of pharmacy practice}, 25(5):343--350.
\newblock Place: England.

\bibitem[Giacobbi et~al., 2018]{giacobbi_guided_2018}
Giacobbi, P.~J., \textbf{Long, D.M.}, Nolan, R., Shawley, S., Johnson, K., and Misra, R.
  (2018).
\newblock Guided imagery targeting exercise, food cravings, and stress: a
  multi- modal randomized feasibility trial.
\newblock {\em Journal of behavioral medicine}, 41(1):87--98.
\newblock Place: United States.

\bibitem[Havens et~al., 2018]{havens_tenofovir_2018}
Havens, P.~L., \textbf{Long, D.M.}, Schuster, G.~U., Gordon, C.~M., Price, G., Wilson,
  C.~M., Kapogiannis, B.~G., Mulligan, K., and Stephensen, C.~B. (2018).
\newblock Tenofovir disoproxil fumarate appears to disrupt the relationship of
  vitamin {D} and parathyroid hormone.
\newblock {\em Antiviral therapy}, 23(7):623--628.
\newblock Place: England.

\bibitem[LeMasters et~al., 2018]{lemasters_receipt_2018}
LeMasters, T., Madhavan, S.~S., Sambamoorthi, U., Hazard-Jenkins, H.~W., Kelly,
  K.~M., and \textbf{Long, D.M.} (2018).
\newblock Receipt of {Guideline}-{Concordant} {Care} {Among} {Older} {Women}
  {With} {Stage} {I}-{III} {Breast} {Cancer}: {A} {Population}-{Based} {Study}.
\newblock {\em Journal of the National Comprehensive Cancer Network : JNCCN},
  16(6):703--710.
\newblock Place: United States.

\bibitem[Merlin et~al., 2018a]{merlin_brief_2018}
Merlin, J.~S., \textbf{Long, D.M.}, Becker, W.~C., Cachay, E.~R., Christopoulos, K.~A.,
  Claborn, K., Crane, H.~M., Edelman, E.~J., Harding, R., Kertesz, S.~G.,
  Liebschutz, J.~M., Mathews, W.~C., Mugavero, M.~J., Napravnik, S.,
  C~O'Cleirigh, C., Saag, M.~S., Starrels, J.~L., and Gross, R. (2018a).
\newblock Brief {Report}: {The} {Association} of {Chronic} {Pain} and
  {Long}-{Term} {Opioid} {Therapy} {With} {HIV} {Treatment} {Outcomes}.
\newblock {\em Journal of acquired immune deficiency syndromes (1999)},
  79(1):77--82.
\newblock Place: United States.

\bibitem[Merlin et~al., 2018b]{merlin_randomized_2018}
Merlin, J.~S., Westfall, A.~O., \textbf{Long, D.M.}, Davies, S., Saag, M., Demonte, W.,
  Young, S., Kerns, R.~D., Bair, M.~J., Kertesz, S., Turan, J.~M., Kilgore, M.,
  Clay, O.~J., Starrels, J., Pekmezi, D., and Johnson, M.~O. (2018b).
\newblock A {Randomized} {Pilot} {Trial} of a {Novel} {Behavioral}
  {Intervention} for {Chronic} {Pain} {Tailored} to {Individuals} with {HIV}.
\newblock {\em AIDS and behavior}, 22(8):2733--2742.
\newblock Place: United States.

\bibitem[Reed et~al., 2018]{reed_population_2018}
Reed, R.~D., Sawinski, D., Shelton, B.~A., MacLennan, P.~A., Hanaway, M.,
  Kumar, V., \textbf{Long, D.M.}, Gaston, R.~S., Kilgore, M.~L., Julian, B.~A., Lewis,
  C.~E., and Locke, J.~E. (2018).
\newblock Population {Health}, {Ethnicity}, and {Rate} of {Living} {Donor}
  {Kidney} {Transplantation}.
\newblock {\em Transplantation}, 102(12):2080--2087.
\newblock Place: United States.

\bibitem[Dionne-Odom et~al., 2019]{dionne-odom_hiv_2019}
Dionne-Odom, J., Khan, M.~J., Jauk, V.~C., Szychowski, J., \textbf{Long, D.M.},
  Wallace, S., Neely, C., Fry, K., Marrazzo, J., Crain, M., and Tita, A. T.~N.
  (2019).
\newblock {HIV} {Status} and {Other} {Risk} {Factors} for {Prevalent} and
  {Incident} {Sexually} {Transmitted} {Infection} during {Pregnancy}
  (2000-2014).
\newblock {\em Infectious diseases in obstetrics and gynecology}, 2019:6584101.
\newblock Place: Egypt.

\bibitem[Felicione et~al., 2019]{felicione_pilot_2019}
Felicione, N.~J., Enlow, P., Elswick, D., \textbf{Long, D.M.}, Sullivan, C.~R., and Blank,
  M.~D. (2019).
\newblock A pilot investigation of the effect of electronic cigarettes on
  smoking behavior among opioid-dependent smokers.
\newblock {\em Addictive behaviors}, 91:45--50.
\newblock Place: England.

\bibitem[Jaeger et~al., 2019]{jaeger_oblique_2019}
Jaeger, B.~C., Long, D.~L., \textbf{Long, D.M.}, Sims, M., Szychowski, J.~M., Min,
  Y.-I., Mcclure, L.~A., Howard, G., and Simon, N. (2019).
\newblock {OBLIQUE} {RANDOM} {SURVIVAL} {FORESTS}.
\newblock {\em The annals of applied statistics}, 13(3):1847--1883.
\newblock Place: United States.

\bibitem[Long et~al., 2019]{long_investigation_2019}
Long, D.~L., Howard, G., \textbf{Long, D.M.}, Judd, S., Manly, J.~J., McClure, L.~A.,
  Wadley, V.~G., Safford, M.~M., Katz, R., and Glymour, M.~M. (2019).
\newblock An {Investigation} of {Selection} {Bias} in {Estimating} {Racial}
  {Disparity} in {Stroke} {Risk} {Factors}.
\newblock {\em American journal of epidemiology}, 188(3):587--597.
\newblock Place: United States.

\bibitem[Merlin et~al., 2019]{merlin_marijuana_2019}
Merlin, J.~S., \textbf{Long, D.M.}, Becker, W.~C., Cachay, E.~R., Christopolous, K.~A.,
  Claborn, K.~R., Crane, H.~M., Edelman, E.~J., Lovejoy, T.~I., Mathews, W.~C.,
  Morasco, B.~J., Napravnik, S., O'Cleirigh, C., Saag, M.~S., Starrels, J.~L.,
  Gross, R., and Liebschutz, J.~M. (2019).
\newblock Marijuana {Use} {Is} {Not} {Associated} {With} {Changes} in {Opioid}
  {Prescriptions} or {Pain} {Severity} {Among} {People} {Living} {With} {HIV}
  and {Chronic} {Pain}.
\newblock {\em Journal of acquired immune deficiency syndromes (1999)},
  81(2):231--237.
\newblock Place: United States.

\bibitem[Olfert et~al., 2019]{olfert_feasibility_2019}
Olfert, M.~D., Barr, M.~L., Hagedorn, R.~L., \textbf{Long, D.M.}, Haggerty, T.~S.,
  Weimer, M., Golden, J., Maurer, M.~A., Cochran, J.~D., Hendershot, T.,
  Whanger, S.~L., Mason, J.~D., and Hodder, S.~L. (2019).
\newblock Feasibility of a {mHealth} {Approach} to {Nutrition} {Counseling} in
  an {Appalachian} {State}.
\newblock {\em Journal of personalized medicine}, 9(4):E50.
\newblock Place: Switzerland.

\bibitem[Sohail et~al., 2019]{sohail_data_2019}
Sohail, M., Rastegar, J., \textbf{Long, D.M.}, Rana, A., Levitan, E.~B., Reed-Pickens, H.,
  Batey, D.~S., Ross-Davis, K., Gaddis, K., Tarrant, A., Parmar, J., Raper,
  J.~L., and Mugavero, M.~J. (2019).
\newblock Data for {Care} ({D4C}) {Alabama}: {Clinic}-{Wide} {Risk}
  {Stratification} {With} {Enhanced} {Personal} {Contacts} for {Retention} in
  {HIV} {Care} via the {Alabama} {Quality} {Management} {Group}.
\newblock {\em Journal of acquired immune deficiency syndromes (1999)}, 82
  Suppl 3:S192--S198.
\newblock Place: United States.


\bibitem[Figaro et~al., 2020]{figaro_racial_2020}
Figaro, M.~K., \textbf{Long, D.M.}, May, M.~E., Ndetan, H., Cook, A., and Conway, R.~B.
  (2020).
\newblock Racial {Variation} in the {Relationship} of {Glycemic} {Control} with
  {Fracture} {Risk} in {Elderly} {Patients} with {Diabetes}.
\newblock {\em Diabetes, metabolic syndrome and obesity : targets and therapy},
  13:4153--4155.
\newblock Place: New Zealand.

\bibitem[Fobian et~al., 2020a]{fobian_retraining_2020}
Fobian, A.~D., \textbf{Long, D.M.}, and Szaflarski, J.~P. (2020a).
\newblock Retraining and control therapy for pediatric psychogenic
  non-epileptic seizures.
\newblock {\em Annals of clinical and translational neurology},
  7(8):1410--1419.
\newblock Place: United States.

\bibitem[Fobian et~al., 2020b]{fobian_effects_2020}
Fobian, A.~D., Rouse, J., Stager, L.~M., \textbf{Long, D.M.}, Schwebel, D.~C., and Avis,
  K.~T. (2020b).
\newblock The effects of sleep deprivation and text messaging on pedestrian
  safety in university students.
\newblock {\em Sleep}, 43(9):zsaa057.
\newblock Place: United States.

\bibitem[Lappan et~al., 2020]{lappan_longitudinal_2020}
Lappan, S., Thorne, C.~B., \textbf{Long, D.M.}, and Hendricks, P.~S. (2020).
\newblock Longitudinal and {Reciprocal} {Relationships} {Between}
  {Psychological} {Well}- {Being} and {Smoking}.
\newblock {\em Nicotine \& tobacco research : official journal of the Society
  for Research on Nicotine and Tobacco}, 22(1):18--23.
\newblock Place: England.

\bibitem[O'Hara~Tompkins et~al., 2020]{ohara_tompkins_translating_2020}
O'Hara~Tompkins, N., Northrup, K., Grant, J., Weikle, M.~F., \textbf{Long, D.M.}, Bassler,
  J., Workman, C., Ramsey, Z., Jarrett, T., Sirk, H., and Cottrell, L. (2020).
\newblock Translating {School} {Physical} {Education} and {Activity} {Policies}
  into {Practice}: {A} {Case} {Study}.
\newblock {\em Translational journal of the American College of Sports
  Medicine}, 5(12).
\newblock Place: United States.

\bibitem[Slawek et~al., 2020]{slawek_increasing_2020}
Slawek, D.~E., Merlin, J.~S., Owens, M.~A., \textbf{Long, D.M.}, Gonzalez, C.~E.,
  White, D.~M., Lopez, S.~A., Heath, S.~L., and Goodin, B.~R. (2020).
\newblock Increasing age is associated with elevated circulating interleukin-6
  and enhanced temporal summation of mechanical pain in people living with
  {HIV} and chronic pain.
\newblock {\em Pain Reports}, 5(6):e859.
\newblock Publisher: LWW.

\bibitem[Sohail et~al., 2020]{sohail_estimating_2020}
Sohail, M., Levitan, E.~B., Rana, A.~I., Heath, S.~L., Rastegar, J., Kempf,
  M.-C., and \textbf{Long, D.M.} (2020).
\newblock Estimating the {First} 90 of the {UNAIDS} 90-90-90 {Goal}: {A}
  {Review}.
\newblock {\em Journal of the International Association of Providers of AIDS
  Care}, 19:2325958220919290.
\newblock Place: United States.

\bibitem[Van~Gerwen et~al., 2020]{van_gerwen_prevalence_2020}
Van~Gerwen, O.~T., Jani, A., \textbf{Long, D.M.}, Austin, E.~L., Musgrove, K., and
  Muzny, C.~A. (2020).
\newblock Prevalence of {Sexually} {Transmitted} {Infections} and {Human}
  {Immunodeficiency} {Virus} in {Transgender} {Persons}: {A} {Systematic}
  {Review}.
\newblock {\em Transgender health}, 5(2):90--103.
\newblock Place: United States.

\bibitem[Webel et~al., 2020]{webel_prosper-hiv_2020}
Webel, A.~R., \textbf{Long, D.M.}, Rodriguez, B., Davey, C.~H., Buford, T.~W., Crane,
  H.~M., Mayer, K., Saag, M.~S., and Willig, A.~L. (2020).
\newblock The {PROSPER}-{HIV} {Study}: {A} {Research} {Protocol} to {Examine}
  {Relationships} {Among} {Physical} {Activity}, {Diet} {Intake}, and
  {Symptoms} in {Adults} {Living} {With} {HIV}.
\newblock {\em The Journal of the Association of Nurses in AIDS Care : JANAC},
  31(3):346--352.
\newblock Place: United States.

\bibitem[Allman et~al., 2021]{allman_novel_2021}
Allman, P.~H., Aban, I., \textbf{Long, D.M.}, Bridges, S. L.~J., Srinivasasainagendra,
  V., MacKenzie, T., Cutter, G., and Tiwari, H.~K. (2021).
\newblock A novel {Mendelian} randomization method with binary risk factor and
  outcome.
\newblock {\em Genetic epidemiology}, 45(5):549--560.
\newblock Place: United States.

\bibitem[Files et~al., 2021a]{files_sustained_2021}
Files, J.~K., Boppana, S., Perez, M.~D., Sarkar, S., Lowman, K.~E., Qin, K.,
  Sterrett, S., Carlin, E., Bansal, A., Sabbaj, S., \textbf{Long, D.M.}, Kutsch, O.,
  Kobie, J., Goepfert, P.~A., and Erdmann, N. (2021a).
\newblock Sustained cellular immune dysregulation in individuals recovering
  from {SARS}-{CoV}-2 infection.
\newblock {\em The Journal of clinical investigation}, 131(1):140491.
\newblock Place: United States.

\bibitem[Files et~al., 2021b]{files_duration_2021}
Files, J.~K., Sarkar, S., Fram, T.~R., Boppana, S., Sterrett, S., Qin, K.,
  Bansal, A., \textbf{Long, D.M.}, Sabbaj, S., Kobie, J.~J., Goepfert, P.~A., and
  Erdmann, N. (2021b).
\newblock Duration of post-{COVID}-19 symptoms is associated with sustained
  {SARS}- {CoV}-2-specific immune responses.
\newblock {\em JCI insight}, 6(15):151544.
\newblock Place: United States.

\bibitem[Fobian et~al., 2021]{fobian_transient_2021}
Fobian, A.~D., \textbf{Long, D.M.}, Bryan, D., Hunter, G., and Gower, B.~A. (2021).
\newblock Transient effect of aerobic exercise training on insulin sensitivity.
\newblock {\em Diabetes Epidemiology and Management}, 4:100032.
\newblock Publisher: Elsevier.

\bibitem[LaRowe et~al., 2021]{larowe_prevalence_2021}
LaRowe, L.~R., Cleveland, J.~D., \textbf{Long, D.M.}, Nahvi, S., Cachay, E.~R.,
  Christopoulos, K.~A., Crane, H.~M., Cropsey, K., Napravnik, S., O'Cleirigh,
  C., Merlin, J.~S., and Ditre, J.~W. (2021).
\newblock Prevalence and impact of comorbid chronic pain and cigarette smoking
  among people living with {HIV}.
\newblock {\em AIDS care}, 33(12):1534--1542.
\newblock Place: England.

\bibitem[McKetchnie et~al., 2021]{mcketchnie_effectiveness_2021}
McKetchnie, S.~M., O'Cleirigh, C., Crane, H.~M., Hill, S.~V., Prior, D.,
  Peretti, M., Parman, M., Levy, D.~E., \textbf{Long, D.M.}, and Cropsey, K. (2021).
\newblock Effectiveness of a smoking cessation algorithm integrated into {HIV}
  primary care: {Study} protocol for a randomized controlled trial.
\newblock {\em Contemporary clinical trials}, 110:106551.
\newblock Place: United States.

\bibitem[Molina et~al., 2021]{molina_psychological_2021}
Molina, K., Baskin, M.~L., \textbf{Long, D.M.}, and Carson, T.~L. (2021).
\newblock Psychological and behavioral pathways between perceived stress and
  weight change in a behavioral weight loss intervention.
\newblock {\em Journal of behavioral medicine}, 44(6):822--832.
\newblock Place: United States.

\bibitem[Wallace et~al., 2021]{wallace_prevalence_2021}
Wallace, D.~M., Alcaide, M.~L., Wohlgemuth, W.~K., Jones~Weiss, D.~L.,
  Uribe~Starita, C., Patel, S.~R., Stosor, V., Levine, A., Skvarca, C., Long,
  D.~M., Rubtsova, A., Adimora, A.~A., Gange, S.~J., Spence, A.~B., Anastos,
  K., Aouizerat, B.~E., Anziska, Y., and Punjabi, N.~M. (2021).
\newblock Prevalence and correlates of restless legs syndrome in men living
  with {HIV}.
\newblock {\em PloS one}, 16(10):e0258139.
\newblock Place: United States.

\bibitem[Allman et~al., 2022]{allman_mendelian_2022}
Allman, P.~H., Aban, I., \textbf{Long, D.M.}, Patki, A., MacKenzie, T., Irvin, M.~R.,
  Lange, L.~A., Lange, E., Cutter, G., and Tiwari, H.~K. (2022).
\newblock Mendelian randomization in the multivariate general linear model
  framework.
\newblock {\em Genetic epidemiology}, 46(1):17--31.
\newblock Place: United States.

\bibitem[Anderson et~al., 2022]{anderson_university_2022}
Anderson, J.~L., Reamey, R.~A., Levitan, E.~B., M~Asif, I., S~Aswani, M.,
  Fletcher, F.~E., G~Hall, A., Kennedy, K.~C., \textbf{Long, D.M.}, Redden, D., Tunagur,
  A., Wasko, M., Willig, J., Wyatt, M., and Mugavero, M.~J. (2022).
\newblock The {University} of {Alabama} at {Birmingham} {COVID}-19
  {Collaborative} {Outcomes} {Research} {Enterprise}: {Developing} an
  institutional learning health system in response to the global pandemic.
\newblock {\em Learning health systems}, 6(2):e10292.
\newblock Place: United States.

\bibitem[Budhwani et~al., 2022a]{budhwani_mhealth_2022}
Budhwani, H., Enah, C., Bond, C.~L., Halle-Ekane, G., Wallace, E., Turan,
  J.~M., Szychowski, J.~M., \textbf{Long, D.M.}, Carlo, W.~A., Tih, P.~M., and Tita, A.
  T.~N. (2022a).
\newblock {mHealth} {Phone} {Intervention} to {Reduce} {Maternal} {Deaths} and
  {Morbidity} in {Cameroon}: {Protocol} for {Translational} {Adaptation}.
\newblock {\em International journal of women's health}, 14:677--686.
\newblock Place: New Zealand.

\bibitem[Budhwani et~al., 2022b]{budhwani_gaps_2022}
Budhwani, H., Hao, J., Maragh-Bass, A.~C., Hill, S.~V., \textbf{Long, D.M.}, and
  Simpson, T. (2022b).
\newblock Gaps in sexually transmitted infection screening among youth living
  with {HIV} in {Alabama}.
\newblock {\em BMC research notes}, 15(1):347.
\newblock Place: England.

\bibitem[Budhwani et~al., 2022c]{budhwani_adapting_2022}
Budhwani, H., Paulino-Ramirez, R., Waters, J., Bond, C.~L., Ruiz, I., Long,
  D.~M., Varas-Diaz, N., Naar, S., Nyblade, L., and Turan, J.~M. (2022c).
\newblock Adapting and pilot testing an {HIV} and intersectional stigma
  reducing intervention for {Dominican} {Republic} healthcare contexts:
  {Protocol} for translational research.
\newblock {\em Contemporary clinical trials communications}, 29:100980.
\newblock Place: Netherlands.

\bibitem[Budhwani et~al., 2022d]{budhwani_developing_2022}
Budhwani, H., Sharma, V., \textbf{Long, D.M.}, and Simpson, T. (2022d).
\newblock Developing a {Clinic}-{Based}, {Vaccine}-{Promoting} {Intervention}
  for {African} {American} {Youth} in {Rural} {Alabama}: {Protocol} for a
  {Pilot} {Cluster}-{Randomized} {Controlled} {Implementation} {Science}
  {Trial}.
\newblock {\em JMIR research protocols}, 11(4):e33982.
\newblock Place: Canada.

\bibitem[Elliott et~al., 2022]{elliott_somatic_2022}
Elliott, L.~C., Stager, L.~M., \textbf{Long, D.M.}, Goodin, B.~R., and Fobian, A.~D.
  (2022).
\newblock Somatic {Symptoms} in {Adolescents} {With} an {Ill} {Parent}.
\newblock {\em Psychosomatic medicine}, 84(4):421--428.
\newblock Place: United States.

\bibitem[Hao et~al., 2022]{hao_missed_2022}
Hao, J., \textbf{Long, D.M.}, Relyea-Ashley, H.~M., Budhwani, H., Simpson, T.~Y., and
  Hill, S.~V. (2022).
\newblock Missed clinic visits in youth living with {HIV} in {Alabama}: {A}
  {Cohort} {Study}.
\newblock Pre-print.

\bibitem[Janorkar et~al., 2022]{janorkar_association_2022}
Janorkar, D.~A., \textbf{Long, D.M.}, Weber, K.~M., Sharma, A., Lin, G.-H., D'Souza,
  G., Edmonds, A., Kassaye, S., Lahiri, C.~D., and Konkle-Parker, D. (2022).
\newblock Association between {BMI} and periodontitis in women living with or
  at risk for {HIV}.
\newblock {\em Special care in dentistry : official publication of the American
  Association of Hospital Dentists, the Academy of Dentistry for the
  Handicapped, and the American Society for Geriatric Dentistry},
  42(5):486--493.
\newblock Place: United States.

\bibitem[Knittel et~al., 2022]{knittel_self-reported_2022}
Knittel, A.~K., Rudolph, J.~E., Shook-Sa, B.~E., Edmonds, A., Ramirez, C.,
  Cohen, M., Taylor, T., Adedimeji, A., Michel, K.~G., Milam, J., Cohen, J.,
  Donohue, J.~D., Foster, A., Fischl, M.~A., \textbf{Long, D.M.}, and Adimora, A.~A.
  (2022).
\newblock Self-{Reported} {Sexually} {Transmitted} {Infections} {After}
  {Incarceration} in {Women} with or at {Risk} for {HIV} in the {United}
  {States}, 2007-2017.
\newblock {\em Journal of women's health (2002)}, 31(3):382--390.
\newblock Place: United States.

\bibitem[Shook-Sa et~al., 2022]{shook-sa_estimating_2022}
Shook-Sa, B.~E., Hudgens, M.~G., Knittel, A.~K., Edmonds, A., Ramirez, C.,
  Cole, S.~R., Cohen, M., Adedimeji, A., Taylor, T., Michel, K.~G., and
  {others} (2022).
\newblock Estimating {Point} {Exposure} {Effects} on {Count} {Outcomes} with
  {Observational} {Data}.
\newblock {\em arXiv preprint arXiv:2202.01650}.

\bibitem[Siddiqui et~al., 2022]{siddiqui_risk_2022}
Siddiqui, M., Moore, T.~J., \textbf{Long, D.M.}, Burkholder, G.~A., Willig, A., Wyatt,
  C., Heath, S., Muntner, P., and Overton, E.~T. (2022).
\newblock Risk {Factors} for {Incident} {Hypertension} {Within} 1 {Year} of
  {Initiating} {Antiretroviral} {Therapy} {Among} {People} with {HIV}.
\newblock {\em AIDS research and human retroviruses}, 38(9):735--742.
\newblock Place: United States.

\bibitem[Simonsson et~al., 2022]{simonsson_prevalence_2022}
Simonsson, O., Goldberg, S.~B., Chambers, R., Osika, W., \textbf{Long, D.M.}, and
  Hendricks, P.~S. (2022).
\newblock Prevalence and associations of classic psychedelic-related seizures
  in a population-based sample.
\newblock {\em Drug and alcohol dependence}, 239:109586.
\newblock Place: Ireland.



\bibitem[Sohail et~al., 2022b]{sohail_partnership_2022}
Sohail, M., \textbf{Long, D.M.}, Batey, D.~S., Mugavero, M.~J., Ojesina, A.~I., and
  Levitan, E.~B. (2022b).
\newblock Partnership status and time to viral suppression and sustained viral
  suppression among newly diagnosed heterosexual people with {HIV}.
\newblock {\em International journal of STD \& AIDS}, 33(4):347--354.
\newblock Place: England.

\bibitem[Spieler et~al., 2022]{spieler_trends_2022}
Spieler, G., Westfall, A.~O., \textbf{Long, D.M.}, Cherrington, A., Burkholder, G.~A.,
  Funderburg, N., Raper, J.~L., Overton, E.~T., and Willig, A.~L. (2022).
\newblock Trends in diabetes incidence and associated risk factors among people
  with {HIV} in the current treatment era.
\newblock {\em AIDS (London, England)}, 36(13):1811--1818.
\newblock Place: England.

\bibitem[Walker et~al., 2022]{walker_leveraging_2022}
Walker, J., Heudebert, J.~P., Patel, M., Cleveland, J.~D., Westfall, A.~O.,
  Dempsey, D.~M., Guzman, A., Zinski, A., Agarwal, M., \textbf{Long, D.M.}, Willig, J.,
  and Lee, R. (2022).
\newblock Leveraging {Technology} and {Gamification} to {Engage} {Learners} in
  a {Microbiology} {Curriculum} in {Undergraduate} {Medical} {Education}.
\newblock {\em Medical science educator}, 32(3):649--655.
\newblock Place: United States.

\bibitem[Bassler et~al., 2023]{bassler_development_2023}
Bassler, J.~R., Cagle, I., Crear, D., Kay, E.~S., \textbf{Long, D.M.}, Mugavero, M.~J.,
  Nassel, A.~F., Ostrenga, L., Parman, M., Preg, S., Wang, X., Batey, D.~S.,
  Rana, A., and Levitan, E.~B. (2023).
\newblock Development and implementation of a distributed data network between
  an academic institution and state health departments to investigate variation
  in time to {HIV} viral suppression in the {Deep} {South}.
\newblock {\em BMC public health}, 23(1):937.
\newblock Place: England.

\bibitem[Gagnon et~al., 2023]{gagnon_delivery_2023}
Gagnon, K.~W., Baral, S., \textbf{Long, D.M.}, Guzman, A.~L., Johnson, B., Burkholder, G.,
  Willig, J., Mugavero, M., Baldwin, M., Fogger, S., Creger, T., Cropsey, K.,
  and Eaton, E. (2023).
\newblock Delivery of the {HIV} {Service} and {Telemedicine} {Through}
  {Effective} {Patient}- {Reported} {Outcomes} (+{STEP}) {Intervention} to
  {Increase} {Screening} and {Treatment} of {Mental} {Health} and {Substance}
  {Use} {Disorders} for {People} {Living} {With} {HIV} in {Alabama}: {Protocol}
  for an {Effectiveness}-{Implementation} {Study}.
\newblock {\em JMIR research protocols}, 12:e40470.
\newblock Place: Canada.

\bibitem[Howell et~al., 2023]{howell_real-world_2023}
Howell, C.~R., Bradley, H., Zhang, L., Cleveland, J.~D., \textbf{Long, D.M.}, Horton, T.,
  Krantz, O., Mugavero, M.~J., Williams, W.~L., Amerson, A., and Cherrington,
  A.~L. (2023).
\newblock Real-world integration of the protocol for responding to and
  assessing patients' assets, risks, and experiences tool to assess social
  determinants of health in the electronic medical record at an academic
  medical center.
\newblock {\em Digital health}, 9:20552076231176652.
\newblock Place: United States.

\bibitem[Isehunwa et~al., 2023]{isehunwa_multicomponent_2023}
Isehunwa, O.~O., Hill, S.~V., Menninger, A.~T., Hubner, B., Krakower, D., Long,
  D.~M., Pratt, M.~C., Clement, M.~E., Wagoner, N.~V., Lanzi, R.~G., Simpson,
  T., Elopre, L., and Matthews, L.~T. (2023).
\newblock A {Multicomponent} {Intervention} to {Train} and {Support} {Family}
  {Medicine} {Providers} to {Promote} {Pre}-exposure {Prophylaxis} ({PrEP}) for
  {Adolescent} {Girls} and {Young} {Women} in the {Deep} {South}: {Protocol}
  for the {PrEP}-{Pro} {Study}.
\newblock {\em JMIR research protocols}, 12:e44908.
\newblock Place: Canada.

\bibitem[Matthews et~al., 2023a]{matthews_geospatial_2023}
Matthews, L.~T., \textbf{Long, D.M.}, Bassler, J., Nassel, A., Levitan, E.~B., Heath,
  S.~L., Rastegar, J., Pratt, M.~C., and Kempf, M.-C. (2023a).
\newblock Geospatial {Analysis} of {Time} to {Human} {Immunodeficiency} {Virus}
  ({HIV}) {Diagnosis} and {Adult} {HIV} {Testing} {Coverage} {Highlights}
  {Areas} for {Intervention} in the {US} {Southeast}.
\newblock {\em Open forum infectious diseases}, 10(3):ofad107.
\newblock Place: United States.

\bibitem[McCollum et~al., 2023]{mccollum_social_2023}
McCollum, C.~G., Carodine, A., Chiedo, A., Penney, B., \textbf{Long, D.M.}, Blumenfeld,
  R., Smith, A., Hill, S., Herbey, I.~I., Rana, A., and Elopre, L. (2023).
\newblock Social {Support} {Assets} and {Needs} of {Underrepresented}
  {Students} {Participating} in {Health} {Sciences} {Pathways} {Programs} in
  {Birmingham}, {Alabama}.
\newblock {\em Journal of acquired immune deficiency syndromes (1999)},
  94(2S):S99--S107.
\newblock Place: United States.

\bibitem[Muzny et~al., 2023]{muzny_impact_2023}
Muzny, C.~A., Van~Gerwen, O.~T., Schroeder, J.~A., Kay-Duncan, E.~S., Siwakoti,
  K., Aaron, K.~J., Eastlund, I.~C., Graves, K.~J., Elnaggar, J.~H., Tamhane,
  A., \textbf{Long, D.M.}, Van~Wagoner, N., Toh, E., and Taylor, C.~M. (2023).
\newblock Impact of testosterone use on the vaginal microbiota of transgender
  men, including susceptibility to bacterial vaginosis: study protocol for a
  prospective, observational study.
\newblock {\em BMJ open}, 13(3):e073068.
\newblock Place: England.

\bibitem[Sohail et~al., 2023a]{sohail_role_2023}
Sohail, M., \textbf{Long, D.M.}, Kay, E., Levitan, E.~B., Batey, D.~S., Reed-Pickens, H.,
  Rana, A., Carodine, A., Nevin, C., Eady, S., Parmar, J., Turner, K., Orakwue,
  I., Miller, T., Wynne, T., and Mugavero, M. (2023a).
\newblock Role of {Visit} {Modality} in the {HIV}-{Related} {No}-{Shows}
  {During} the {COVID}-19 {Pandemic}: {A} {Multisite} {Retrospective} {Cohort}
  {Study}.
\newblock {\em AIDS and behavior}, 27(8):2478--2487.
\newblock Place: United States.

\bibitem[Sohail et~al., 2023b]{sohail_partnership_2023}
Sohail, M., \textbf{Long, D.M.}, Mugavero, M.~J., Batey, D.~S., Ojesina, A.~I., and
  Levitan, E.~B. (2023b).
\newblock Partnership status and retention in care among cisgender heterosexual
  newly diagnosed people with {HIV}: a cohort study.
\newblock {\em AIDS care}, 35(9):1428--1436.
\newblock Place: England.

\bibitem[Sohail et~al., 2023c]{sohail_assessing_2023}
Sohail, M., Mugavero, M., \textbf{Long, D.M.}, Levitan, E.~B., Batey, D.~S., Reed-Pickens,
  H., Rana, A., Carodine, A., Nevin, C.~R., Eady, S., Parmar, J., Turner, K.,
  Orakwue, I., Miller, T., Wynne, T., and Kay, E.~S. (2023c).
\newblock Assessing the {Impact} of {COVID}-19 on {Retention} in {HIV}
  {Primary} {Care}: {A} {Longitudinal} {Multisite} {Analysis}.
\newblock {\em AIDS and behavior}, 27(5):1514--1522.
\newblock Place: United States.

\bibitem[Stager et~al., 2023]{stager_parenting_2023}
Stager, L.~M., Watson, C., \textbf{Long, D.M.}, and Fobian, A.~D. (2023).
\newblock Parenting {Factors} {Predicting} {Longitudinal} {Fast}-{Food}
  {Consumption} {From} {Adolescence}.
\newblock {\em American Journal of Lifestyle Medicine}, page 15598276231208032.
\newblock Publisher: SAGE Publications Sage CA: Los Angeles, CA.

\bibitem[Turner et~al., 2023]{turner_implementation_2023}
Turner, W.~H., Kay, E.~S., Raper, J.~L., Musgrove, K., Gaddis, K., Ferrell, A.,
  Yester, D., Glenn, J., Atwater, M., Hutchins, K., Tamhane, A., \textbf{Long, D.M.},
  Kellar, P., Creger, T., Eaton, E., and Willig, A.~L. (2023).
\newblock Implementation of a {Novel} {Clinic}/{Community} {Partnership}
  {Addressing} {Food} {Insecurity} {Among} {Adults} {With} {HIV} in the
  {Southern} {United} {States}: {A} {Program} {Brief}.
\newblock {\em The Journal of the Association of Nurses in AIDS Care : JANAC},
  34(3):307--315.
\newblock Place: United States.

\bibitem[Walker et~al., 2023]{walker_attitudes_2023}
Walker, K.~W., Mugo, N., Ngure, K., Gakuo, S., Casmir, E., Wiener, H., Long,
  D., Shrestha, S., and Marrazzo, J. (2023).
\newblock Attitudes {Toward} {Menstrual} {Suppression} {Among} {Cyclic} and
  {Continuous} {Contraceptive} {Vaginal} {Ring} {Users} in {Kenya}.
\newblock {\em Journal of Family \& Reproductive Health}.

\bibitem[Webel et~al., 2023]{webel_physical_2023}
Webel, A.~R., Davey, C.~H., Oliveira, V., Cleveland, D., Crane, H.~M.,
  Gripshover, B.~M., \textbf{Long, D.M.}, Fleming, J.~G., Buford, T.~W., and Willig,
  A.~L. (2023).
\newblock Physical activity is associated with adiposity in older adults with
  {HIV} in the modern {HIV} era.
\newblock {\em AIDS (London, England)}, 37(12):1819--1826.
\newblock Place: England.

\bibitem[Budhwani et~al., 2024]{budhwani_viral_2024}
Budhwani, H., Hao, J., Maragh-Bass, A.~C., Hill, S., \textbf{Long, D.M.}, and Simpson,
  T. (2024).
\newblock Viral load and sexually transmitted infection testing among youth
  with {HIV} in a southern {United} {States} clinic.
\newblock {\em International journal of STD \& AIDS}, 35(1):11--17.
\newblock Place: England.

\bibitem[Dionne et~al., 2024]{dionne_trimethoprim-sulfamethoxazole_2024}
Dionne, J.~A., Anchang-Kimbi, J., Hao, J., \textbf{Long, D.M.}, Apinjoh, T., Tih, P.,
  Mbah, R., Ngah, E.~N., Juliano, J.~J., Kahn, M., Bruxvoort, K., Van Der~Pol,
  B., Tita, A. T.~N., Marrazzo, J., and Achidi, E. (2024).
\newblock Trimethoprim-{Sulfamethoxazole} {Plus} {Azithromycin} to {Prevent}
  {Malaria} and {Sexually} {Transmitted} {Infections} in {Pregnant} {Women}
  {With} {HIV} ({PREMISE}): {A} {Randomized}, {Double}-{Masked},
  {Placebo}-{Controlled}, {Phase} {IIB} {Clinical} {Trial}.
\newblock {\em Open forum infectious diseases}, 11(5):ofae274.
\newblock Place: United States.


\bibitem[Hao et~al., 2024]{hao_characteristics_2024}
Hao, J., \textbf{Long, D.M.}, Relyea~Ashley, H.~M., Budhwani, H., Simpson, T.~Y., and
  Hill, S.~V. (2024).
\newblock The {Characteristics} of {Youth} {With} {Missed} {HIV} {Visits} in
  {Alabama}.
\newblock {\em Open forum infectious diseases}, 11(3):ofae086.
\newblock Place: United States.


\bibitem[Hill et~al., 2024]{hill_re-evaluating_2024}
Hill, S.~V., Hao, J., Newlin-Bradner, M., \textbf{Long, D.M.}, Budhwani, H., and
  Simpson, T. (2024).
\newblock Re-evaluating the relationship between youth with {HIV} and {BMI} in
  an age of increasing rates of overweight and obese youth.
\newblock {\em BMC research notes}, 17(1):97.
\newblock Place: England.


\bibitem[Matthews et~al., 2024]{matthews_implementation_2024}
Matthews, L.~T., Owembabazi, M., Tukwasibwe, D., Najjuma, A., Muyindike, W.,
  Tumwine, J.~M., Hornstein, B., Bassler, J., \textbf{Long, D.M.}, Gill, E., Young, C.,
  Chitneni, P., Psaros, C., Kanyesigye, M., Kato~Kalyebara, P., Kaida, A., and
  Bwana, M. (2024).
\newblock Implementation of a safer conception programme for {HIV}-affected men
  and women in rural {Uganda}.
\newblock {\em Global public health}, 19(1):2342023.
\newblock Place: England.



\bibitem[Muzny et~al., 2024]{muzny_microbial_2024}
Muzny, C.~A., Elnaggar, J.~H., Sousa, L. G.~V., Lima, A., Aaron, K.~J.,
  Eastlund, I.~C., Graves, K.~J., Dong, C., Van~Gerwen, O.~T., Luo, M.,
  Tamhane, A., \textbf{Long, D.M.}, Cerca, N., and Taylor, C.~M. (2024).
\newblock Microbial interactions among {Gardnerella}, {Prevotella} and
  {Fannyhessea} prior to incident bacterial vaginosis: protocol for a
  prospective, observational study.
\newblock {\em BMJ open}, 14(2):e083516.
\newblock Place: England.


\bibitem[Sims et~al., 2024a]{sims_population-average_2024}
Sims, A., Long, D.~L., Tiwari, H.~K., Cui, J., Long, D.~M., Brown, T.~M.,
  Smith, M.~J., and Levitan, E.~B. (2024a).
\newblock Population-average mediation analysis for zero-inflated count
  outcomes.
\newblock {\em Statistics in medicine}, 43(13):2547--2559.
\newblock Place: England.

\bibitem[Sims et~al., 2024b]{sims_application_2024}
Sims, A., Tiwari, H., Levitan, E.~B., \textbf{Long, D.M.}, Howard, G., Brown, T., Smith,
  M.~J., Cui, J., and Long, D.~L. (2024b).
\newblock Application of marginalized zero-inflated models when mediators have
  excess zeroes.
\newblock {\em Statistical methods in medical research}, 33(1):148--161.
\newblock Place: England.


\bibitem[Vazquez~Guillamet et~al., 2024]{vazquez_guillamet_acceptability_2024}
Vazquez~Guillamet, L.~J., Babey, M.~M., Njah, M., Blake, H., Jasani, A., Kyeng,
  R., Hao, J., \textbf{Long, D.M.}, Tih, P., Turan, J.~M., Khan, E.~M., and Dionne, J.
  (2024).
\newblock Acceptability, feasibility and potential of an intervention using
  secret {Facebook} groups to complement existing {HIV} prevention strategies
  among female sex workers in {Cameroon}, a randomized pilot study.
\newblock {\em AIDS care}, 36(4):517--527.
\newblock Place: England.

\bibitem[Konkle-Parker et~al., 2024]{konkle-parker_population_nodate}
Konkle-Parker, D., Cleveland, D., \textbf{Long, D.M.}, Nair, V., Fischl, M.~A., Wingood,
  G., and Edmonds, A.
\newblock Population density and health outcomes in women with {HIV}: {A}
  retrospective longitudinal analysis.
\newblock {\em Journal of Women’s Health}, (Accepted: March 21, 2024).

\bibitem[Yigit et~al., 2024]{yigit_moderated_2024}
Yigit, I., Paulina-Ramirez, R., Waters, J., \textbf{Long, D.M.}, Turan, J.~M., and
  Budhwani, H. (2024).
\newblock A moderated mediation analysis of {HIV} and intersectional stigmas
  and antiretroviral adherence in people living with {HIV} in the {Dominican}
  {Republic}.
\newblock {\em AIDS and Behavior}, (Accepted: June 18, 2024).




\end{thebibliography}
